Bicycle Balance Assistance Reduces Probability of Falling at Low Speeds When Subjected to Mechanical Perturbations

### 2024-04-24 main.tex
Use example images.
Fix quotes.

\begin{figure}
  \centering
  % TODO : scale these pngs to a reasonable size for an A4 sheet
  \subcaptionbox{}{\includegraphics[width=70mm]{figures/participant-in-set-up.png}}
  \subcaptionbox{Diagram of perturbation system.}{\includegraphics[width=70mm]{figures/setup-diagram.png}
}
\end{figure}

@@

Subjects wore a helmet and fall safety harness attached to the ceiling. We
allowed them practice riding on the treadmill until they indicated they were
comfortable enough to have perturbations applied. For most, this was less than a
10~\si{\minute} warm up. We then asked the rider to ride for 90~\si{\second},
attempting to maintain the location of their front wheel on the center line of
the treadmill. We define a "fall" on the treadmill by two criteria: the rider
removes their foot from the pedal and places it on the ground or the bicycle
wheel exceeds the width of the treadmill. We then applied perturbations in
random directions (clockwise or counter clockwise) increasing the magnitude by
X~\si{\newton\meter} each time. We log the magnitude that causes the first fall
to characterize that subject's nominal fall threshold. Following this we apply
20 perturbations of random magnitudes to the cyclist while they ride at a
constant speed and record which perturbations cause a fall. We let the cyclist
rest and then perform another 20 perturbations. We randomize whether the
balance assist system is on or off during the first or second set of
perturbations.

@@

\todo[inline]{Marten writes "The skill variable is not included, because it was
not collected correctly for all participants." This needs to be addressed. What
about skill being tied to participant clusters?}

>>>>

\begin{figure}
  \centering
  % TODO : scale these pngs to a reasonable size for an A4 sheet
  %\subcaptionbox{}{\includegraphics[width=70mm]{figures/participant-in-set-up.png}}
  \subcaptionbox{}{\includegraphics[width=70mm]{example-image-a}}
  %\subcaptionbox{Diagram of perturbation system.}{\includegraphics[width=70mm]{figures/setup-diagram.png}
  \subcaptionbox{Diagram of perturbation system.}{\includegraphics[width=70mm]{example-image-b}
}
\end{figure}

@@

Subjects wore a helmet and fall safety harness attached to the ceiling. We
allowed them practice riding on the treadmill until they indicated they were
comfortable enough to have perturbations applied. For most, this was less than a
10~\si{\minute} warm up. We then asked the rider to ride for 90~\si{\second},
attempting to maintain the location of their front wheel on the center line of
the treadmill. We define a ``fall'' on the treadmill by two criteria: the rider
removes their foot from the pedal and places it on the ground or the bicycle
wheel exceeds the width of the treadmill. We then applied perturbations in
random directions (clockwise or counter clockwise) increasing the magnitude by
X~\si{\newton\meter} each time. We log the magnitude that causes the first fall
to characterize that subject's nominal fall threshold. Following this we apply
20 perturbations of random magnitudes to the cyclist while they ride at a
constant speed and record which perturbations cause a fall. We let the cyclist
rest and then perform another 20 perturbations. We randomize whether the
balance assist system is on or off during the first or second set of
perturbations.

@@

\todo[inline]{Marten writes ``The skill variable is not included, because it
was not collected correctly for all participants.'' This needs to be addressed.
What about skill being tied to participant clusters?}
